---
title: "Cabbages"
author: "Jason Leon"
date: "6/5/23"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Now with ggplot - first select the basic data

```{r}
library(ggplot2)

# Create the box plot
ggplot(veggy, aes(x = Cult, y = VitC)) +
  geom_boxplot() +
  labs(x = "Cult", y = "VitC") +
  ggtitle("Box Plot of VitC by Cult") +
  theme(plot.title = element_text(hjust = 0.5, size = 16))
```

when we look at the 2 box plot. The major box is above the lower one. the middle is 50% of the method of the higher box and is quite a bit different from the c39 and 52. they are complete apart from each other. we think will find a statistical difference with the 2 method.



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

After looking at the stats it shows that the average amount of c39 is 51.0 and the average for c52 is 64.5. The numerical difference is showed in the amount and c52 and c39 don't overlap every other.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

  
```{r}
t.test(VitC~Cult,data=veggy)
```
The chances of getting the result that we got which was .000000003405 is a small number. when comparing c39 and c52 the vitamin is very low.it is very possible that it might happen but a low chance. The hypothesis is to be rejected.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Today we created box plot and we used chat GPT to help us make the box plot. we also commented on the box plot and the charts we got from chat gpt. we also learned how to read the Ttest result ans explain it in simple terms that anyone can also understand.